Communication in Agile Inter-team Development

### 2019-01-21 Draft/Parts/Main.tex
Finishing half thoughts.

\section{Communication Concerns}\label{sec:spt_ex} 
%overview
A fundamental issue with tasking teams with different goals is that teams can become isolated with respect to the context of their work.
% problem
Consider a scenario at Spotify \cite{kniberg12}: a tester on a particular agile team invested time to solve a particular problem, which was also faced by another tester on a different team. Without communication, these team members would perform redundant work.
To address this problem Spotify defines Chapters, which are crosscutting groups which gather individuals with similar roles across different Squads. 
At Spotify \cite{kniberg12}, offices are laid out so that the Squads making up a Tribe are spatially close. This leads to an environment where an informal exchange of information on the Tribe's work will occur.
%Although larger than Squads (7-10 members), Tribes are limited in size (< 100) to ensure smooth communication.
%todo: any more issues? Dunbar

In general, consistency becomes an issue when expanding to multiple teams.
The product owner in an agile process model is the person with the project vision, and with a small team, the product owner can clearly communicate this to every team member.
Members can even query the product owner directly when in doubt.
However, in large projects where multiple teams are working together, it is practically impossible for the owner to continue what they did in a small team.
This motivates a need for a formal definition of their vision as it gives teams something to consult to when encountering a design decision.

@@

\subsection{Process Adaptations} 
\label{sec:proc_impv}
	There are many changes \cite{collabAcrossAgile_article} that can be incorporated into a process model to decrease the chance that parallel agile teams run into problems during integration.

@@

\subsection{Technology Improvements} \label{sec:tech_impv}
Selecting an appropriate technology stack plays an important role in maintaining a distributed development environment.
Technology enables communication and task management so that teams can work together efficiently.
%The following are areas where technology can enable a more efficient agile process.

>>>>

\section{Communication Concerns}\label{sec:spt_ex} 
%overview
A fundamental issue in tasking teams with separate goals is that teams can become isolated from other teams pursuing similar or related goals.
% problem
Consider a scenario at Spotify \cite{kniberg12}: a tester on a particular agile team invested time to solve a particular problem, which was also faced by another tester on a different team. Without communication, these team members would perform redundant work.
To address this problem Spotify defines Chapters, which are crosscutting groups which gather individuals with similar roles across different Squads. 
At Spotify \cite{kniberg12}, offices are laid out so that the Squads making up a Tribe are spatially close.
This leads to an environment where an informal exchange of information on the Tribe's work will occur.
Although larger than Squads (7-10 members), Tribes are limited in size (< 100) to ensure smooth communication.
%todo: any more issues? Dunbar

In general, consistency becomes an issue when expanding to multiple teams.
The product owner in an agile process model is the person with the project vision, and with a small team, the product owner can clearly communicate this to every team member.
Members can even query the product owner directly when in doubt.
However, in large projects where multiple teams are working together, it is practically impossible for the owner to continue what they did in a small team.
This motivates a need for a formal definition of their vision as it gives teams something to consult to when encountering a design decision.
Without a functional specification, teams will be unable to produce components which can be integrated.

@@

\subsection{Process Adaptations} 
\label{sec:proc_impv}
	There are many changes \cite{collabAcrossAgile_article} that can be incorporated into a process model to decrease the chance that parallel agile teams run into problems during development or integration.

@@

\subsection{Technology Improvements} \label{sec:tech_impv}
Selecting an appropriate technology stack plays an important role in enabling communication and task management so that teams can work together efficiently.
%The following are areas where technology can enable a more efficient agile process.
